Sex, education, and mental health: Analyzing American census data through statistical methods, 2018 to 2021

### 2024-10-24 paper/paper.qmd
Corrected line 412 and 320 to remove

max_count <- max(table(labeled_df_reduced_2018$sex)) + 1000
labeled_df_reduced_2018 |> 
  ggplot(aes(x = sex)) +
  geom_histogram(stat = "count", fill = "#013065", color = "white") +
  scale_y_continuous(limits = c(0, max_count)) +
  geom_text(
    stat = "count", 
    color = "black",
    aes(label = after_stat(count)), 
    vjust = -0.3,  # Adjust vertical position of labels
    size = 5       # Adjust size of labels
  ) +
  labs(title = "Sex", 
       x = "Sex", 
       y = "Frequency") +
  theme_light()+
  theme(
    plot.title = element_text(size = 20, face = "bold"),  # Title font size
    axis.title.x = element_text(size = 16),               # X-axis label size
    axis.title.y = element_text(size = 16),               # Y-axis label size
    axis.text = element_text(size = 14)                   # Axis text size (ticks)
  )
max_count <- max(table(labeled_df_reduced_2021$sex)) + 1000
labeled_df_reduced_2021 |> 
  ggplot(aes(x = sex)) +
  geom_histogram(stat = "count", fill = "#013065", color = "white") +
  scale_y_continuous(limits = c(0, max_count)) +
  geom_text(
    stat = "count", 
    color = "black",
    aes(label = after_stat(count)), 
    vjust = -0.3,  # Adjust vertical position of labels
    size = 5       # Adjust size of labels
  ) +
  labs(title = "Sex", 
       x = "Sex", 
       y = "Frequency") +
  theme_light()+
  theme(
    plot.title = element_text(size = 20, face = "bold"),  # Title font size
    axis.title.x = element_text(size = 16),               # X-axis label size
    axis.title.y = element_text(size = 16),               # Y-axis label size
    axis.text = element_text(size = 14)                   # Axis text size (ticks)
  )
```

>>>>

max_count <- max(table(labeled_df_reduced_2018$sex)) + 1000
labeled_df_reduced_2018 |> 
  ggplot(aes(x = sex)) +
  geom_histogram(stat = "count", fill = "#013065", color = "white") +
  scale_y_continuous(limits = c(0, max_count)) +
  geom_text(
    stat = "count", 
    color = "black",
    aes(label = after_stat(count)), 
    vjust = -0.3,  # Adjust vertical position of labels
    size = 5       # Adjust size of labels
  ) +
  labs(title = " ", 
       x = "Sex", 
       y = "Frequency") +
  theme_light()+
  theme(
    plot.title = element_text(size = 20, face = "bold"),  # Title font size
    axis.title.x = element_text(size = 16),               # X-axis label size
    axis.title.y = element_text(size = 16),               # Y-axis label size
    axis.text = element_text(size = 14)                   # Axis text size (ticks)
  )
max_count <- max(table(labeled_df_reduced_2021$sex)) + 1000
labeled_df_reduced_2021 |> 
  ggplot(aes(x = sex)) +
  geom_histogram(stat = "count", fill = "#013065", color = "white") +
  scale_y_continuous(limits = c(0, max_count)) +
  geom_text(
    stat = "count", 
    color = "black",
    aes(label = after_stat(count)), 
    vjust = -0.3,  # Adjust vertical position of labels
    size = 5       # Adjust size of labels
  ) +
  labs(title = " ", 
       x = "Sex", 
       y = "Frequency") +
  theme_light()+
  theme(
    plot.title = element_text(size = 20, face = "bold"),  # Title font size
    axis.title.x = element_text(size = 16),               # X-axis label size
    axis.title.y = element_text(size = 16),               # Y-axis label size
    axis.text = element_text(size = 14)                   # Axis text size (ticks)
  )
```
